%!TEX root = paper.tex
\section{Introduction}

% What are transactive energy systems
% What is the key challenge : decentralized information architecture
% What is the related research
% What are the contributions of this paper
% What is the outline of this paper

Power grids are undergoing major changes due to rapid acceleration in
renewable energy resources, such as wind and solar power
\cite{5430489}.
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. 
%At the same time,
%battery technology costs per kWh have dropped significantly
%\cite{stock2015powerful}, reaching grid parity.
% \cite{bronski2015economics}
The massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\emph{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,melton2013gridwise}. Transactive % NOTE: removed cox2013structured to save space
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} on the same
feeder (\emph{i.e.}, those sharing a power line link) can operate in
an open market, trading and exchanging generated energy
locally. \emph{Distribution System Operators} (DSOs) can be the
custodians of this market, while still meeting the net demand
\cite{7462854}. For example, the Brooklyn Microgrid
(\url{brooklynmicrogrid.com}) is a peer-to-peer market for locally
generated renewable energy, which was developed by LO3 Energy as a pilot project.

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as IoT
applications in smart grids~\cite{Haider2016166}. The transactive grid
described in this paper is the next step in the evolution of energy
systems \cite{collier2017emerging}.

In general, the focus is now on creating a distributed IoT
infrastructure that provides the necessary computation fabric to
support the interplay between energy control and fiscal market
challenges, as shown by Volttron \cite{katipamula2016volttron},
OpenFMB \cite{gunthersmart}, and the Resilient Information
Architecture Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, and do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and focuses on the following privacy challenges:
\begin{itemize}[itemsep=0.1\parskip,topsep=-0.75\parskip]
\item \textbf{Leakage of energy usage patterns to other prosumers}
  Since prosumers may purchase energy from each other in a transactive
  microgrid, transactions may inadvertently reveal the prosumers'
  detailed energy usage patterns to other prosumers within the
  microgrid.  Addressing this issue in a decentralized trading system
  is hard as it requires hiding the identities of trade partners from
  each other. In comparison, secure smart metering reveals the
  prosumers' energy usage patterns only to the operator.

\item \textbf{Inference of future states of a prosumer} Transactions
  may reveal the future energy usage of a prosumer, which could be
  used to infer private information.  For example, a smart home may
  know that its inhabitants will go out in the evening (\emph{e.g.},
  by looking at their calendar), and it may trade energy futures
  accordingly in the morning.  Without adequate privacy measures,
  these trades may reveal to other prosumers in the microgrid that the
  inhabitants will not be at home later.  Note that energy futures,
  whose delivery may happen several hours after when the transaction
  is made, can play an important role in predicting and controlling
  microgrid load.  In comparison, smart metering reveals only current
  (or past) usage.

\item \textbf{Personally identifiable information} Transactions and
  energy usage data in a transactive microgrid are much richer sources
  of information than the simple usage data collected by smart meters.
  In particular, the information available in a transactive microgrid
  is a superset of what is available from smart metering and may be
  used to infer personal information, such as risk propensity and
  financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy systems can be deployed widely in practice,
the privacy issues described above must be addressed.  Addressing
these issues is hard, however, since solutions must also satisfy
security and safety requirements, which often conflict with privacy
goals.  For example, to prevent a prosumer from destabilizing the
system through careless of malicious energy trading, a transactive
grid must check all of the prosumer's transactions.  In a
decentralized system, these checks require disseminating information,
which could be used to infer the prosumer's future energy consumption.

This paper introduces %an overview of the transactive sequence between
%different components of the systems. We also describe the structure of
%these transactions and show how they can be used to provide
\emph{Privacy-preserving Energy Transactions} (PETra), which is our
distributed-ledger based solution that (1) enables trading energy
futures in a secure and verifiable manner, (2) preserves prosumer
privacy, and (3) enables DSOs to regulate trading and enforce certain
safety rules.
%
This paper is organized as follows: we first describe
the basic components of a transactive IoT microgrid and formulate
security, safety, and privacy requirements; we next introduce PETra
and describe the transactions and services used to implement it; we
then discuss how it satisfies the security, safety, and privacy
requirements; finally, we 
%compare our work on PETra with 
describe related work
and present concluding remarks.

