%!TEX root = paper.tex
\section{Introduction}

% What are transactive energy systems
% What is the key challenge : decentralized information architecture
% What is the related research
% What are the contributions of this paper
% What is the outline of this paper

Power grids are undergoing major changes due to rapid
acceleration in renewable energy resources, such as wind and solar power \cite{5430489}. 
% \cite{EIA2014}
For example, $4,\!143$ megawatts of solar panels were installed in the
third quarter of 2016 \cite{seia}. This capacity is estimated to grow
from 4\% in 2015 to 29\% in 2040 \cite{Randal}. At the same time,
battery technology costs per kWh have dropped significantly
\cite{stock2015powerful}, reaching grid parity.
%\cite{bronski2015economics}
This massive integration of renewable energy requires detailed
information and visibility into all aspects of the network, making it
hard to manage, especially in the presence of variable distributed
energy resources \cite{7452738}. A different vision for the future of
power-grid operations is therefore emerging: {\em a decentralized
  system in which local communities are arranged in microgrids}
\cite{rahimi2012transactive}. In this vision, energy generation,
transmission, distribution, and even storage (\em{e.g.}, electric
vehicles in a community) can be strategically used to balance load and
demand spikes.

Furthering the concept of microgrids, transactive energy models have
been proposed to support the next distribution system evolution
\cite{kok2016society,cox2013structured,melton2013gridwise}. Transactive
energy is a set of market-based constructs for dynamically balancing
the demand and supply across the electrical infrastructure
\cite{melton2013gridwise}. In this approach, customers on the same
feeder (\em{i.e.}, those sharing a power line link) can operate in an
open market, trading and exchanging generated energy
locally. Distribution System Operators (DSOs) can be the custodian of
this market, while still meeting the net demand \cite{7462854}. For
example, the Brooklyn Microgrid, which was developed by LO3 Energy as
a pilot project, is a peer-to-peer market for locally generated
renewable energy.\footnote{\url{http://brooklynmicrogrid.com/}}

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
the next step for the smart grid.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible. 

In general, the focus is now on creating a distributed IoT
infrastructure
%  comprising of smart meters, feeders, smart inverters, utility substations, the utility central offices, and the transmission system operator
that provides the necessary computation fabric to support the
interplay between energy control and fiscal market challenges, as
shown by Volttron \cite{katipamula2016volttron}, OpenFMB
\cite{gunthersmart}, and the Resilient Information Architecture
Platform for Smart Grid (RIAPS)
\cite{eisele2017riaps,Scott2017ICCPS}. For instance, the latter is a
distributed IoT operating system that provides the foundations for all
algorithms, isolates the hardware details from the algorithms, and
provides essential mechanisms for resource management, fault
tolerance, and security. Most of these efforts, however, focus on the
computation and distribution of information, but do not provide the
support required to handle the privacy challenges that arise from the
required information exchange in this decentralized transactive
system.

This paper assumes the existence of a distributed IoT infrastructure
and specifically focus on the following privacy challenges:
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\em{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later, which could be a security risk.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play a important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

% Abhishek, can you please add a pithy summary of this challenge?
\item \bf{Pithy challenge summary needed.} Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

Before transactive energy system can be deployed widely in practice,
we must address the privacy issues described above.  Addressing these
issues is hard, however, since solutions also must satisfy security
and safety requirements, which often conflict with privacy goals.  For
example, to prevent a prosumer from destabilizing the grid through
careless of malicious energy trading, the system must check all of the
prosumer's transactions.  In a decentralized system, this requires
disseminating information, which could be used to infer the prosumer's
future energy consumption.

\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
  sure what you mean by ``such a service.''}  \Abhishek{We should
  connect the paper and our work back to IoT in this paragraph.}  This
paper proposes a solution that (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules.  \Aron{Since SIGCHI does not have section numbers, this
  paragraph, which describes the organization of the paper, is not
  very clear.}  We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  We next introduce a decentralized system for
transactive microgrids based on distributed ledgers and describe the
transactions and services used to implement this system.  We then
discuss how the system satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

